Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-02-20 Ben_Manuscripts/transport/Outline.tex
Updates to outline

  The 4 ketone-like molecules tested show a range of transport behaviors.
  \begin{itemize}
    \item Urea, Acetic Acid, Acetamide and Acetone are all characterized by a carbonyl group
    with two attached heavy atoms. 
    \item All have approximately the same molecular weight and are planar molecules due to
    the sp2 hybridization of the carbonyl group.
    \item The fastest solute of this grouping, Urea, has an MSD comparable to that of ethylene
    glycol while the slowest, Acetone, has an MSD one third of that of Urea.
  \end{itemize}

  Once again, the trends in the MSD can in large part be explained by the solutes'
  ability to hydrogen bond.  % or maybe just polarity
  \begin{itemize}
  	\item Urea, Acetic Acid and Acetamide are all capable of donating hydrogen bonds,
  	while acetone is the first instance of a molecule in this study that can only
  	accept hydrogen bonds.
  	\item Urea has two hydrogen bond donor nitrogen atoms. It is not surprising that
  	its density is high near the pore center, particularly near the monomer head groups.
  	\item Acetamide has only one nitrogen atom. One of two peaks in its density is 
  	located close to the peak of Urea, likely corresponding to hydrogen bonds with head groups.
  	A second peak is located within the head group region. %BJC: hbonds with ethers vs. head groups. Or is it just planarity?
  	\item Acetic acid, a carboxylic acid shows a relatively high density in the pore region, with 
  	a peak close to the carboxylate groups.  %BJC: hbonds with 
  	\item Acetone is stabilized by accepting hydrogen bonds from water in the pore region, but
    its low polarity and planar shape gives it comparable stability when trapped between head groups.
%  	\item Acetone's has two prominent peaks in its radial density. One is in the pore region and the o
%  	other is relatively deep in the head group region.
  \end{itemize}

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.45\textwidth]{ketone_rdf.pdf}
  \caption{}\label{fig:ketones_rdf}
  \end{figure}

@@

  \noindent Mercaptoethanol has a similar average RDF and MSD to ethylene glycol.
  \begin{itemize}
    \item There is a much larger uncertainty associated with mercaptoethanol's MSD.
    \item It spends more time in the tail region than ethylene glycol, where transport
    is inherently slower, and may contribute to some slower MSDs.  % Can quantify as a percentage
    \item Conversely, Mercaptoethanol also exhibits some of the highest single solute MSDs % BJC: hypothesis about observation. Remains to be quantified
    \item It hydrogen bonds with head groups 6 times less frequently than ethylene glycol.
    % Dwell time as a function of hbonds?
    \item Some of this can be accounted for by the higher density of mercaptoethanol 
    molecules in the head group / tail region.
    \item When both hydroxyl groups of ethylene glycol are hydrogen bonded with the a
    monomer head group simultaneously,

@@

@@

  The radial density functions highlight the solutes' preference for the 
  pore region.
  \begin{itemize}
  	\item There are small peaks in the radial density greater than 1 nm 
  	from the pore center.
  	\item The solutes become trapped in these regions where each step is
  	highly anti-correlated to its previous step, leading to very low MSDs.
  	\item The large size and nonplanar shapes of ethyl acetate and propylene 
  	carbonate may destabilize entrapment in the tail region more quickly, leading
  	to slightly faster transport. 
  	% BJC:  Ethyl acetate spends all of its time in a linear or near-linear conformation.
%  	\item The relatively small amount of movement on the timescales studied 
%  	do not reveal definitive reasons
  	\item Overall, 
  \end{itemize}

>>>>

  The 4 ketone-like molecules tested show a surprising range of transport behaviors.
  \begin{itemize}
    \item Urea, Acetic Acid, Acetamide and Acetone are all characterized by a carbonyl group
    with two attached heavy atoms. 
    \item All have approximately the same molecular weight and are planar molecules due to
    the sp2 hybridization of the carbonyl group.
    \item The fastest solute of this grouping, Urea (comparable to Acetic Acid too), has an
    MSD comparable to that of ethylene glycol while the slowest, Acetone, has an MSD one 
    third of that of Urea.
  \end{itemize}

  Once again, the trends in the MSD can in large part be explained by the solutes'
  preference for water.
  \begin{itemize}
  	\item Urea, Acetic Acid and Acetamide are all capable of donating hydrogen bonds,
  	while acetone is the first instance of a molecule in this study that can only
  	accept hydrogen bonds. It follows that acetone has the slowest MSD of this grouping.
  	\item Urea and Acetamide both have hydrogen bond donating nitrogen atoms, however
  	nitrogen is a weaker hydrogen bond donor than oxygen due to its lower electronegativity.
  	\item Hence, Acetic Acid donates the greatest number of hydrogen bonds and has
  	the highest density throughout the pore region.
  	\item With two nitrogen groups that hydrogen bond relatively infrequently, one might 
  	expect Urea to exhibit much faster transport, however its MSD is comparable to
  	the much stickier acetic acid. 
  	\item Urea is highly soluble in water but not miscible in all proportions like 
  	acetic acid or even acetone.
  	\item Relative to acetic acid, acetamide, urea and acetone spend more time in the head group region.
  	\item There is a large peak near the head groups, but \% of the urea molecules 
  	are behind in the head group region.
  	\item The structure of acetamide differs from acetic acid only by an amine group in place
  	of a hydroxyl group.
  	\item The weaker hydrogen bonding capability of acetamide and an extra nonpolar methyl group compared to
  	Urea makes acetamide even more likely to partition. 
  	\item Urea has two hydrogen bond donor nitrogen atoms. It is not surprising that
  	its density is high near the pore center, particularly near the monomer head groups.

  	\item Acetamide has only one nitrogen atom. One of two peaks in its density is 
  	located close to the peak of Urea, likely corresponding to hydrogen bonds with head groups.
  	A second peak is located within the head group region. %BJC: hbonds with ethers vs. head groups. Or is it just planarity?
  	\item Acetic acid, a carboxylic acid shows a relatively high density in the pore region, with 
  	a peak close to the carboxylate groups.  %BJC: hbonds a lot 
  	\item Acetone is stabilized by accepting hydrogen bonds from water in the pore region, but
    its low polarity and planar shape gives it comparable stability when trapped between head groups.
%  	\item Acetone's has two prominent peaks in its radial density. One is in the pore region and the o
%  	other is relatively deep in the head group region.
  \end{itemize}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ketone_rdf.pdf}
  \caption{}\label{fig:ketones_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ketone_ratio.pdf}
  \caption{}\label{fig:ketones_ratio}
  \end{subfigure}
  \end{figure}

@@

  \noindent Mercaptoethanol has a similar average RDF and MSD to ethylene glycol.
  \begin{itemize}
    \item There is a much larger uncertainty associated with mercaptoethanol's MSD.
    \item It spends more time in the tail region than ethylene glycol, where transport
    is inherently slower, and may contribute to some slower MSDs.  % Can quantify as a percentage
    \item Conversely, Mercaptoethanol also exhibits some of the highest single solute MSDs % BJC: hypothesis about observation. Remains to be quantified
    \item It hydrogen bonds with head groups 6 times less frequently than ethylene glycol.
    % Dwell time as a function of hbonds?
    \item Some of this can be accounted for by the higher density of mercaptoethanol 
    molecules in the head group / tail region. There are nearly 40 \% more mercaptoethanol
    beyond 0.8 nm from the pore center. 
    \item When both hydroxyl groups of ethylene glycol are hydrogen bonded with the a
    monomer head group simultaneously,

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{SOH_trace.pdf}
  \caption{}\label{fig:SOH_trace}
  \end{subfigure}
  \caption{}
  \end{figure}

@@

  The radial density functions highlight the solutes' preference for the 
  head group region.
  \begin{itemize}
  	\item There are small peaks in the radial density greater than 1 nm 
  	from the pore center.
  	\item The solutes become trapped in these regions where each step is
  	highly anti-correlated to its previous step, leading to very low MSDs.
  	\item The large size and nonplanar shapes of ethyl acetate and propylene 
  	carbonate may destabilize entrapment in the tail region more quickly, leading
  	to slightly faster transport. 
  	% BJC:  Ethyl acetate spends all of its time in a linear or near-linear conformation.
%  	\item The relatively small amount of movement on the timescales studied 
%  	do not reveal definitive reasons
  	\item Overall, 
  \end{itemize}
